Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-05-15 manuscript.Rmd
Updated file.  Getting markdown PDF working.

# Read Scopus database
scopus.df <- read.csv("scopus.csv")

@@

abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
abb$ID <- 1:nrow(abb)
sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
    select(-X) %>%
    mutate(Documents = ifelse(Documents == 0, NA, Documents))

# Re-order the factor by Overall.N
title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
    distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()

title.order = title$Abbrev

sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))

# Create labels for the facets
Overall.N <- distinct(sm.scopus.merged, Abbrev) 
lab <- paste("N=", Overall.N$Overall.N, sep="")
xpos = rep(2002, 79)
ypos = rep(215, 79)
ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
    rename(Abbrev = Overall.N.Abbrev)

# Plotting function    
plotSmallMultiples <-  ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
    facet_wrap(~ Abbrev) + 
    geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
    theme_bw() +
    theme(legend.position = "bottom", 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
    ylim(c(0,225)) +
    scale_x_continuous(breaks=seq(1989, 2020, 8))

@@

scopus.df <- read.csv("scopus.csv")
articles.df <-full_join(sm.df, scopus.df, by = c("Journal", "Year"))

@@

```{r}
# Read Scopus database
scopus.df <- read.csv("scopus.csv")

@@

ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) + 
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
  ylim(c(0, 60)) + 
    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1), 
          panel.grid.minor=element_blank(),
         legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("N") + 
    xlab("Year") + 
    labs(fill = "Study type") +
    scale_y_continuous(breaks = seq(0,90, 10))

@@

ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .60, colour = "dimgray") + facet_wrap(~studyType) + 
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .015, .005))

@@

ggplot(na.omit(df1), aes(x = N, y= journal, group = journal, colour = studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
    geom_point(size = 2.5) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank(), legend.position = "none") + 
    xlim(0, 600) + 
    ylab("Journal") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_x_continuous(breaks = seq(0, 60, 10))

@@

ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
    geom_segment(aes(yend = journal), xend=0) +
    geom_point(aes(size = Overall.N.Strength)) + 
    theme_bw() +
    theme(panel.grid.major.y = element_blank(), legend.position = c(.62, .65)) +
    ylab("Journal") +
    xlab("Proportion") +
    labs(size = "Total number of \nEBP articles published")

@@

As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.  The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` (median = `r options(digits=2); median(final.list.updated$study.time);`, sd =  `r options(digits=2); sd(final.list.updated$study.time)`). The overall h-Index for each journal.  The h-Index values represent the current h-Index of each journal, as opposed to the h-Index of the final study period, so these values should be interpreted cautiously.  The mean h-Index value is XXXX, (median = XXX; sd = XXX). A total of `r pretty(sum(articles.year.df$year.count))` article records were obtained across these journals.  The average number of articles per journal was `r options(digits=2); pretty(mean(articles.year.df$year.count))` (median = `r options(digits=2); pretty(median(articles.year.df$year.count))`, sd = `r options(digits=2); pretty(sd(articles.year.df$year.count))`). This figure shows consistent growth in the number of articles from 1989 to 2005.  Notable fluctuations in the number of articles was observed from 2005 to 2008, followed by growth until 2012. The decline from 2012 to 2013 should be interpreted cautiously, as this may be an artifact due to delays in indexing.

Data from the National Science Foundation regarding the number of earned doctorates in social work and social welfare were added to further contextualize the publication trends.  These data reveal both growth and decline in the number of earned doctorates over the period of time for which data were available.  The number of earned doctorates exhibited a rise from 2003 to 2005, which corresponded to a rise in the number of article published during these years.  Between 2008 and 2012, the number of doctoral degrees exhibited a decline, but the number of published articles continued to rise.

@@

```{r finalArticleListecho=FALSE, comment=NA}
print.data.frame(final.list, row.names=FALSE)
```

@@

```{r}
plotIndex
```

@@

```{r}
plot.article.count
```

@@

>>>>

# Read Scopus database
scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")

@@

# sm.scopus.merged.table <- group_by(sm.scopus.merged, Journal) %>%
#     summarize(DataBase.N = sum(N, na.rm=TRUE), Scopus.N = sum(Documents, na.rm=TRUE)) %>%
#     arrange(desc(DatabBase.N))
# 
# data.frame(sm.scopus.merged.table)

# abb <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/master.csv")
# abb$ID <- 1:nrow(abb)
# sm.scopus.merged <- full_join(sm.scopus.merged, abb, by = "Journal") %>% 
#     select(-X) %>%
#     mutate(Documents = ifelse(Documents == 0, NA, Documents))
# 
# # Re-order the factor by Overall.N
# title <- sm.scopus.merged %>% arrange(desc(Overall.N)) %>% 
#     distinct(Abbrev) %>% filter(!is.na(Abbrev)) %>% distinct()
# 
# title.order = title$Abbrev
# 
# sm.scopus.merged$Abbrev <- factor(sm.scopus.merged$Abbrev, levels = (title.order))
# 
# # Create labels for the facets
# Overall.N <- distinct(sm.scopus.merged, Abbrev) 
# lab <- paste("N=", Overall.N$Overall.N, sep="")
# #xpos = rep(2002, 79)
# #ypos = rep(215, 79)
# xpos = rep(2025, 79)
# ypos = rep(25, 79)
# ldata <- data.frame(xpos, ypos, lab, Overall.N$Abbrev) %>% 
#     rename(Abbrev = Overall.N.Abbrev) 
#

# Plotting function    
# plotSmallMultiples <-  ggplot(sm.scopus.merged,  aes(Year, N)) + geom_line(colour="#e66101") +
#     facet_wrap(~ Abbrev) + 
#     geom_line(data = sm.scopus.merged, aes(Year, Documents), group = 1,colour="#5e3c99", alpha=.60) + 
#     theme_bw() +
#     theme(legend.position = "bottom", 
#     panel.grid.minor = element_blank(), 
#     axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
#     geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab), size =3) + 
#     ylim(c(0,225)) +
#     scale_x_continuous(breaks=seq(1989, 2015, 8)) + 
#     expand_limits(x = 2050))

@@

scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")
articles.df <-full_join(sm.df, scopus.df, by = c("Journal", "Year"))

@@

```{r}
# Read Scopus database
scopus.df <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/scopus.csv")

@@

stacked.plot <- ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) + 
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
  ylim(c(0, 60)) + 
    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1), 
          panel.grid.minor=element_blank(),
         legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("N") + 
    xlab("Year") + 
    labs(fill = "Study type") +
    scale_y_continuous(breaks = seq(0,90, 10))

@@

evidence.plot <- ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .60, colour = "dimgray") + facet_wrap(~studyType) + 
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .015, .005))

@@

journal.evidence.plot <- ggplot(na.omit(df1), aes(x = N, y= journal, group = journal, colour = studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
    geom_point(size = 2.5) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank(), legend.position = "none") + 
    xlim(0, 600) + 
    ylab("Journal") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_x_continuous(breaks = seq(0, 60, 10))

@@

EBP.plot <- ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
    geom_segment(aes(yend = journal), xend=0) +
    geom_point(aes(size = Overall.N.Strength)) + 
    theme_bw() +
    theme(panel.grid.major.y = element_blank(), legend.position = c(.62, .65)) +
    ylab("Journal") +
    xlab("Proportion") +
    labs(size = "Total number of \nEBP articles published")

@@

```{r}
# As shown in Table 1, `r nrow(final.list.25)` journals were included in the current study.  The mean number of years of inclusion is `r options(digits=2); mean(final.list.updated$study.time)` (median = `r options(digits=2); median(final.list.updated$study.time);`, sd =  `r options(digits=2); sd(final.list.updated$study.time)`). The overall h-Index for each journal.  The h-Index values represent the current h-Index of each journal, as opposed to the h-Index of the final study period, so these values should be interpreted cautiously.  The mean h-Index value is XXXX, (median = XXX; sd = XXX). A total of `r pretty(sum(articles.year.df$year.count))` article records were obtained across these journals.  The average number of articles per journal was `r options(digits=2); pretty(mean(articles.year.df$year.count))` (median = `r options(digits=2); pretty(median(articles.year.df$year.count))`, sd = `r options(digits=2); pretty(sd(articles.year.df$year.count))`). This figure shows consistent growth in the number of articles from 1989 to 2005.  Notable fluctuations in the number of articles was observed from 2005 to 2008, followed by growth until 2012. The decline from 2012 to 2013 should be interpreted cautiously, as this may be an artifact due to delays in indexing.  
```
Data from the National Science Foundation regarding the number of earned doctorates in social work and social welfare were added to further contextualize the publication trends.  These data reveal both growth and decline in the number of earned doctorates over the period of time for which data were available.  The number of earned doctorates exhibited a rise from 2003 to 2005, which corresponded to a rise in the number of article published during these years.  Between 2008 and 2012, the number of doctoral degrees exhibited a decline, but the number of published articles continued to rise.

@@

```{r finalArticleListecho=FALSE, comment=NA}
#print.data.frame(final.list, row.names=FALSE)
```

@@

```{r}
#plotIndex
```

@@

```{r}
#plot.article.count
```

@@

```{r}
evidence.plot
```
\newpage

```{r}
stacked.plot
```
\newpage
```{r fig.height=9.5}
journal.evidence.plot
```

\newpage
```{r fig.height=9.5}
EBP.plot
```
